%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {World Bank} % Organization
    {United States} % Location
    {Nov. 2020 - Current} % Date(s)
    {
      I'm currently working as a consultant on the Governance team of the Development Impact Evaluation (DIME) department. DIME develops customized data and evidence ecosystems to produce actionable information and recommend specific policy pathways to maximize impact.
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Leading the data platform component of the Microdata \& Evidence for Government (MEGA) global public good initiative, including product management, business development, data engineering, and fundraising
        \item Advising DIME department leadership on data platform and information system strategic investment through the World Bank's ITS capital budget planning process
        \item Leading the project management and software development effort of Arbiter/Cadaster – a mediation case management and analytics platform piloted and since productionized by the Kenyan Judiciary
        \item Leading the functional, technical and architectural design for the modernization of the Information System for Jordan Response Platform for the Syria Crisis (JORISS)
        \item Conceptualizing and co-leading the DIME Digital program through collaboration with Digital Development Global Practice's Global Challenge Program
        \item Designing and implementing impact evaluations through randomized controlled trials (RCTs) of web based interventions in various country context, including Peru, Kenya and France
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-founder \& Software Engineer \& Data Scientist} % Job title
    {Unit.IO} % Organization
    {Singapore} % Location
    {Dec. 2017 - Dec. 2019} % Date(s)
    {
      I co-founded unit.io to build quality software and data science solutions for our academic and corporate clients.
    }

%---------------------------------------------------------
  \cventry
    {Engineering Team Lead} % Job title
    {Quantcast} % Organization
    {Singapore} % Location
    {Sept. 2014 - Nov. 2017} % Date(s)
    {
      Quantcast is a technology company that uses big data to make online advertising more relevant for end users and more effective for advertisers.
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Leading the ad services team responsible for advertising campaign data distribution to bidding servers
        \item Re-architecting the real-time bidding (RTB) configuration data pipeline – from a batch system to an update stream
        \item Two-time prize winner of the company hackathons
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Engineer} % Job title
    {Hive Wallet} % Organization
    {Remote} % Location
    {Jan. 2014 - Sept. 2014} % Date(s)
    {
      Hive brings secure, simple and cross-platform cryptocurrency wallet apps to the consumer market. As a company, Hive honors open source in their source code distribution, and decentralization in software design.
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Leading the frontend and backend development of hive-js, the web wallet that is designed for evergreen browsers
        \item Core developer and maintainer on the most popular open-source bitcoin JavaScript library: bitcoinjs-lib
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Pivotal Labs} % Organization
    {Singapore} % Location
    {Dec. 2011 - Jan. 2014} % Date(s)
    {
      Pivotal is a global agile development consultancy. I was trained to become a consultant to help our clients create their app from scratch while building their engineering team with agile practices and principles.
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Full stack test-driven development of web services
        \item Building data pipeline with Amazon EMR and analytics tools
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
